Fixing Lost JavaScript Function Names in Debuggers

### 2011-03-30 papers/splash-wavefront2011/sigplanconf-template.tex

%\section{The Nameless Function Problem}
\section{The Anonymous Functions Problem}

@@

The other pieces of information which are important at function calls are {\small\texttt{this}} and argument values. In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called. The {\small\texttt{this}} value is missed in both views. The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.

\section{Automated Funcation Naming}
  The problem is discussed in several locations on the web \cite{DisplayName, Zaytsev} and various solutions have been proposed by developers. A simple solution would be annotating the function by its name or adding a property (e.g., \textit{displayName}) with the function name as its value. Although these solutions may help, they cause developers extra work.
	We instead, to tackle the aforementioned issues caused due to the lack of function names, propose automated function naming by anlyzing the source code. Before getting into details of how the function name is constructed, we discuss the rationale behind some of decisions we made in this approach.

\subsection{The Rationale}
\subsubsection{Function Object vs. Function Body}%What Should be Named?}
The first question arises is that which one should be named? the function body or the function object. A function name must help the developer to distinguish the function from other functions with different behaviours. The behaviour of a function object, in addition to its body (the source code), is dependent to the enclosing scopes (e.g., global and closure variables). Although the actual enclosing scopes are not known until the function object creation, their structure can be almost known from the enclosing source code. Therefore, to name a function object, it is fair enough to name its \textit{function body}.

%\subsubsection{Static vs. Dynamic}
%Can we improve the names at runtime?
% function object path in dom model is good candidate for the name but only for persistent objects ?

%\subsubsection{Local vs. Global}

%It is conceivable that two function objects which are created from the same function body have different enclosing scopes and therefore different behaviours.

%, the object bound to {\small\texttt{this}}-depending on the way the function is called-and passed arguments. The first two parameters can be almost known from the source code and are less dependent to the runtime while the last two parameters are usually not known until the function call at runtime.

%\subsubsection{Is it possible to automatically name all functions?}
\subsubsection{What Makes a Good Function Name?}
A function name should be useful for both the developer who are familar with the code and the developer who is not. It should explains the function behaviour, or an abstraction of the function behaviour, or why/where the function is used (e.g., to create object \textit{foo}), or at least works as an identifier.

A function body can be uniquely identified by its location in the source file. A naive proposal for the function name for a function body is a combination of the function file name and line number. Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour. On the other extreme extend, the function body itself can be used as the function identifier. This identifier it too long to be displayed and read by the developer.

JavaScript does not support a packageing mechanism to be used for modular programming. Scripts are loaded from different files and executed within the same or different global objects. Developers usually use objects at the top level to encapsulate properties, objects and functions from a framework or library. The same mechanism can be used to define nested subpackages. As the project size and the number of functions increases, the function name may not be enough to recognize the function. The developer also wants to know the function's library or package name.

@@

\begin{table}
\centering
\scalebox{0.8}{
\renewcommand\arraystretch{2.0}
\begin{tabular}{ | c | l | l | l | m{2.5cm} | l|}
  \hline
   & \multicolumn{4} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
  \hline

   1 &
   &  
   & \multicolumn{2}{|m{2.8cm}|}{
     \raggedright property of a new object in an object literal.}
   & \{ ..., foo: function()\{...\}, ...\}\\ %{\small\begin{verbatim}{ ..., foo: function(){...}, ...}\end{verbatim}} \\ %
   \cline{0-0}\cline{4-6}

	 2 &
	 & \multirow{8}{*}{\hspace{.2cm}\begin{rotate}{90}assigned to a(n)\end{rotate}}
	 & \multicolumn{2}{|m{2.8cm}|}{
	   new array index in an array literal.} 
   & [..., function()\{...\}, ...] \\ 
   \cline{0-0}\cline{4-6}

   3 &
   & 
   &  
   & direct access.
   & bar\textsuperscript{*}.foo = function()\{...\}\\
   \cline{0-0}\cline{5-6}

   4 & \multirow{11}{*}{\hspace{.2cm}\begin{rotate}{90}The function object is\end{rotate}} 
   & 
   & 
   & \raggedright hashmap access by a string. 
   & bar\textsuperscript{*}["foo"] = function()\{...\} \\
   \cline{0-0}\cline{5-6}

   5 &
   & 
   & \multirow{4}{*}{\hspace{.2cm}\begin{rotate}{90}object property through\end{rotate}}
   & \raggedright hashmap access by a variable name.
   & bar\textsuperscript{*}[foo] = function()\{...\} \\
   \cline{0-0}\cline{5-6}

   6 &
   & 
   & 
   & \raggedright hashmap access by a JavaScript expression.
   & bar\textsuperscript{*}[foo\textsuperscript{*}] = function()\{...\} \\
   \cline{0-0}\cline{4-6}

   7 &
   &
   & \multicolumn{2}{|l|}{
      array index.}
   & foo\textsuperscript{*}[0] = function()\{...\} \\
   \cline{0-0}\cline{4-6}

   8 &
   & 
   & \multicolumn{2}{|l|}{
      variable.}
   & foo = function()\{...\} \\
   \cline{0-0}\cline{3-6}

@@

\subsection{The basic idea}
   We employ the fact that developers know many function objects (particularly those which are reused) by the names they can access and call them. 
   On the other hand, it is very likely that the function object is assigned to this name in a place very close to the place the function object is created. Therefore, we analyze the code to find all names that the function object is assigned to them. For cases where the function object is not assigned to a variable or object property but is used to produce other values we keep trakc of the function effect on other identifiers.

>>>>

%\section{The Nameless Function Problem}
\section{Anonymous Functions Problem}

@@

Two other pieces of information which are important at function calls are {\small\texttt{this}} and argument values. In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called. The {\small\texttt{this}} value is missed in both views. The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.

\section{Discussion}
The anonymous functions problem is discussed in several articles and forums on the web \cite{DisplayName, Zaytsev}. Different solutions have been proposed and discussed by practitioners. A basic solution is a mechanism for naming functions by developers without affecting the variables in scopes. For example, a new property (e.g., \textit{displayName}) in the function object can be used for storing the function name, or the function name can be defined by an annotation. Although these solutions may help, they cause developers extra work.

We instead propose an almost automated approach for naming all functions by anlyzing the source code. Before getting into explaining the algorithm details we discuss the rationale behind some of decisions we made in this approach.

\subsection{What Makes a Good Function Name?}
A function name is basicly used to assist the developer to recall or understand the function behaviour. For a dveloper who is already familiar with the function, it works more like an identifier. However, this identifier should be easily recognized by the developer. For example, a naive proposal for the function name is a combination of the function file name and its first line number. Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour.

 On the other hand, for a devloper who does not know the function, a function name should explains the function behaviour, or an abstraction of the function behaviour, or why/where the function is used/defined (e.g., to create the object \textit{foo}). A function name must not be too long that can not be displayed or read by the developer. For example, the function body explains the function behaviour well however it is not an appropriate function name.

\subsection{What Should be Named?} %// Function Object or Function Body}%What Should be Named?}
In JavaScript, functions can be accessed and changed like a regular object. Two function objects which are created from the same function body may have different properties. They also may have different enclosing scopes and therefore different behaviours. The question arises here is which one should be named, the function body or the function object? Although the actual enclosing scopes are not known until the function object creation, their structure can be almost known from the enclosing source code. Therfore the general function behaviour is mainly dependent to its function body and the enclosed function bodies.

\subsection{Context, Package and Function Names}
JavaScript does not support a standard packageing mechanism to be used for modular programming. Scripts are loaded from different files and executed within the same or different global objects. Developers usually use objects at the top level to encapsulate properties, objects and functions from a framework or library. The same mechanism is reused for defining subpackages. As the project size and the number of functions increases, the short function name will not be enough for recognizing the function. The developer also wants the class or the module contains the function. In addition to the package name, knowning the context (the enclosing function body) that contains the function can help in better understanding the function behaviour.

%\subsection{Is it possible to automatically name functions?}
%\subsubsection{Static vs. Dynamic}
% Can we improve the names at runtime?
% function object path in dom model is good candidate for the name but only for persistent objects ?

%\subsubsection{Local vs. Global}
%the object bound to {\small\texttt{this}}-depending on the way the function is called-and passed arguments. The first two parameters can be almost known from the source code and are less dependent to the runtime while the last two parameters are usually not known until the function call at runtime.

%\subsubsection{Is it possible to automatically name all functions?}

@@

\section{Automated Funcation Naming}
%	We instead, to tackle the aforementioned issues caused due to the lack of function names, propose automated function naming by anlyzing the source code. Before getting into details of how the function name is constructed, we discuss the rationale behind some of decisions we made in this approach.
  Developers usually understand and refer to function objects by aliases they use to access them. This fact particularly holds for permanent function objects such as classes and utility functions. However, functions with shorter lifetimes such as closures and callbacks are referred by their roles or purposes in the program. We employ these facts to construct an identifier for a function. We analyse the source code to locate alias(es) which the function object is assigned to. If the list of aliases is not empty we select the most appropriate one based on some ranking rules as the function name. Otherwise, we try to build a name based on the aliases that the function object somehow affect on their values. If there is no such alias then the function object is consumed as an argument in a chain of function calls that does not return any value or as a simple closure. If the case of function calls chain we use the most nested called function name for constructing the identifier. In the case of simple closure, we employ the function(s) identifier inside the closure to construct the identifier.

    %  On the other hand, it is very likely that the function object is assigned to this name in a place very close to the place the function object is created. Therefore, we analyze the code to find all names that the function object is assigned to them. For cases where the function object is not assigned to a variable or object property but is used to produce other values we keep track of the function effect on other identifiers.

\subsection{Examples}

\begin{table}
\centering
\scalebox{0.8}{
\renewcommand\arraystretch{2.0}
\begin{tabular}{ | c | l | l | l | m{2.5cm} | l|}
  \hline
   & \multicolumn{4} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
  \hline 
   1 &
   & 
   &  
   & direct access.
   & bar\textsuperscript{*}.foo = function()\{...\}\\
   \cline{0-0}\cline{5-6}

   2 & \multirow{11}{*}{\hspace{.2cm}\begin{rotate}{90}The function object is\end{rotate}} 
   & 
   & 
   & \raggedright hashmap access by a string. 
   & bar\textsuperscript{*}["foo"] = function()\{...\} \\
   \cline{0-0}\cline{5-6}

   3 &
   & \multirow{8}{*}{\hspace{.2cm}\begin{rotate}{90}assigned to a(n)\end{rotate}}
   & \multirow{5}{*}{\hspace{.2cm}\begin{rotate}{90}object property through\end{rotate}}
   & \raggedright hashmap access by a variable name.
   & bar\textsuperscript{*}[foo] = function()\{...\} \\
   \cline{0-0}\cline{5-6}

   4 &
   & 
   & 
   & \raggedright hashmap access by a JavaScript expression.
   & bar\textsuperscript{*}[foo\textsuperscript{*}] = function()\{...\} \\
   \cline{0-0}\cline{5-6}

   5 &
   &
   &
   & \raggedright  array index.
   & foo\textsuperscript{*}[0] = function()\{...\} \\
   \cline{0-0}\cline{4-6}

   6 &
   & 
   & \multicolumn{2}{|l|}{
      variable.}
   & foo = function()\{...\} \\
   \cline{0-0}\cline{4-6}

   7 &
   &  
   & \multicolumn{2}{|m{2.8cm}|}{
     \raggedright property of a new object in an object literal.}
   & \{ ..., foo: function()\{...\}, ...\}\\ %{\small\begin{verbatim}{ ..., foo: function(){...}, ...}\end{verbatim}} \\ %
   \cline{0-0}\cline{4-6}

	 8 &
	 & 
	 & \multicolumn{2}{|m{2.8cm}|}{
	   new array index in an array literal.} 
   & [..., function()\{...\}, ...] \\ 
   \cline{0-0}\cline{3-6}

@@
